---
title: "Using RBR data"
author: "Jonathan Kennel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Install

Typically one installs using install_github from the package devtools with the following code:
```{r inst, echo=TRUE, eval=FALSE}
library(devtools)
install_github('jkennel/rbr')
```

One can also install from a source file where you choose the appropriate tar.gz file.

```{r a0, echo=TRUE, eval=FALSE}
install.packages(file.choose(), repos = NULL, type = 'source')
```


## Load package
```{r a1dot5, echo=TRUE, eval=TRUE, results='hide', message=FALSE, warning=FALSE}
library(rbr)
```

## Read data from rsk file

This reads a single file.

```{r a1, echo = TRUE, eval = TRUE, warning = FALSE}

file_name_and_path <- '/media/kennel/Data/phd/personnel/pat/syngenta/SYN UW1 Baro P1 - 077653_20150410_1435.rsk'

rbr_data <- read_rbr(db_name = file_name_and_path, use_rbr_tz = FALSE)
nrow(rbr_data)

```


## Read data from rsk file and filter by date

This reads in a single file and filters it by date.

```{r a2, echo = TRUE, eval = TRUE, warning = FALSE}

rbr_data <- filter_rbr( db_name = file_name_and_path, 
                      start_date = '2014-12-20', 
                      end_date = '2014-12-21', 
                      use_rbr_tz = FALSE)
nrow(rbr_data)

```

## Read all files in folder

This reads in all files from a folder.

```{r a3, echo = TRUE, eval = TRUE, warning = FALSE}

folder_path <- '/media/kennel/Data/phd/personnel/pat/syngenta'
rbr_data <- read_rbr_folder(folder_path, use_rbr_tz = FALSE)
nrow(rbr_data)

```


## Read all files in folder and filter by date

This reads in all files from a folder.

```{r a4, echo = TRUE, eval = TRUE, warning = FALSE}

rbr_data <- filter_rbr_folder(folder_path, 
                      start_date = '2014-12-20', 
                      end_date = '2014-12-21',
                      use_rbr_tz = FALSE)
nrow(rbr_data)

```


## Read a set of files given a vector of file names and paths.


```{r a5, echo = TRUE, eval = TRUE, warning = FALSE}

# get the first three file names and paths from the folder
(files <- list.files(folder_path, full.names = TRUE, pattern = '*.rsk')[1:3])

rbr_data <- read_rbr_files(files, use_rbr_tz = FALSE)
nrow(rbr_data)

```



## Read a set of files given a vector of file names and paths and filters by date.


```{r a6, echo=TRUE, eval = TRUE, warning = FALSE}

rbr_data <- filter_rbr_files(files, 
                      start_date = '2014-12-20', 
                      end_date = '2014-12-21', 
                      use_rbr_tz = FALSE)

nrow(rbr_data)

```

## List .rsk info

```{r a61, echo=TRUE, eval = TRUE, warning = FALSE}
info <- rbr_info(file_name_and_path)
(info)
```

## List tables in .rsk

```{r a7, echo=TRUE, eval = TRUE, warning = FALSE}
db <- dplyr::src_sqlite(file_name_and_path)

nm_tbl <- dplyr::src_tbls(db)

(nm_tbl)

```

## List fields for each table in .rsk

```{r a8, echo=TRUE, eval = TRUE, warning = FALSE}

lapply(nm_tbl, function(x) dplyr::tbl(db,x))

```
